

```{r parametersChildDocument}

	## required input parameters
    message("Check required input parameters")

	# check if all require input parameters are specified
	variablesToSpecify <- c("dataset", "variables", "covariate")
	inputParametersNotSpecified <- !sapply(variablesToSpecify, exists, where = environment())
	if(any(inputParametersNotSpecified))
		stop("Please specify the ", toString(variablesToSpecify[inputParametersNotSpecified]), ".")

```
	
```{r parametersChildDocumentDefaults}
			
	## optional input parameters, set to default value if not specified
    if(!exists("boxPlot", where = environment())) boxPlot <- TRUE
    if(!exists("histogram", where = environment())) histogram <- TRUE
	if(!exists("pairwiseComparison", where = environment())){
		if(length(variables) > 1 & exists("covariate", where = environment())){
			pairwiseComparison <- TRUE
		}else	pairwiseComparison <- FALSE
	}
	if(length(variables) <= 1) pairwiseComparison <- FALSE
	if(pairwiseComparison & !exists("pairwiseComparisonPlotColorVariable", where = environment()))
		pairwiseComparisonPlotColorVariable <- covariate
	
	if(!exists("includeLda", where = environment())){
		if(length(variables) > 2 & exists("covariate", where = environment())){
			includeLda <- TRUE
		}else includeLda <- FALSE
	}
	if(length(variables) <= 2)	includeLda <- FALSE
	if(includeLda & !exists("covariateLda", where = environment())) covariateLda <- covariate
	if(!exists("typePlot", where = environment()))	typePlot <- "rbokeh"
	
```

```{r compareOutputpathWithWd}

    message("Compare output path with working directory")

	outputPathCompare <- paste0(getwd(), "/")
	if(.Platform$OS.type == "windows") outputPathCompare <- paste0("/", paste(unlist(strsplit(outputPathCompare, split = "/"))[-1], collapse = "/"),"/")

#	differentWd <- outputPath != outputPathCompare
#	
#	if(differentWd) warning(paste0('The specified "outputPath" (i.e. ', outputPath,') is NOT the same \n as the current working directory (i.e. ', outputPathCompare, '). \n', 
#		'The graphs and objects will be saved in the "outputPath" location, \n while the report (and the css file) will be saved in the working directory.'))
	
```

```{r copyCustomCssFile}

    message("Copy css file from package")

#	message("output path css: ", paste0(getwd(), "/css"))

	if(!exists("personalCss", where = environment())) personalCss <- FALSE
	
	if(!personalCss){
		cssFile <- getPathFile("custom.css")
		outputPathCss <- paste0(getwd(), "/css")
		if(.Platform$OS.type == "windows") outputPathCss <- paste0("/", paste(unlist(strsplit(outputPathCss, split = "/"))[-1], collapse = "/"))
		if (!file.exists(outputPathCss)) dir.create(outputPathCss, recursive = TRUE)
		outputPathCss <- paste0(outputPathCss, "/")
		copyFile <- file.copy(from = cssFile, to = outputPathCss, overwrite = TRUE)
	}
  
    message(". Section Material and methods")

```

# Material and methods

## Data

The dataset contains `r nrow(dataset)` samples, `r length(variables)` variables:
`r toString(variables)`
and `r length(covariate)` covariate: `r toString(covariate)`.

```{r detailsOfData}

    message(".. Data table")

	library(DT)
	
	datatable(dataset, 
		options = list(
		searching = TRUE,
		pageLength = 10
#		lengthMenu = c(5, 10, 15, 20)
		),
		rownames = FALSE
	)
	
```

## Summary of the data

Tables below show overall statistics of `r toString(variables)` for:

*  the entire dataset
* the variables for each subset of the `r paste0("'", covariate, "'")`
  covariate:
`r paste(paste("    +", levels(dataset[,covariate])), collapse = "\n")`

<!-- Tables with pander in for loop. -->

```{r summaryDataPander}

  message(".. Summary of the data via pander")

  library(pander)
  panderOptions('knitr.auto.asis', FALSE)
  for(subData in c("all", levels(dataset[,covariate]))){
    
    if(subData == "all"){
      cat("\n### All", tolower(covariate), "\n\n")
      pander(summary(dataset[,variables]), caption = paste("Summary for all", tolower(covariate)))
    }else{
      cat("\n###", simpleCap(subData, onlyFirst = TRUE), "\n\n")
      pander(summary(dataset[dataset[,covariate] == subData,variables]), 
		caption = paste0("Summary for ", subData))
    }
    cat("\n\n")
    
  }

```

`r if(boxPlot)	"# Box plot"`

```{r boxPlots-viaLoopOnChildDocumentInteger, eval = boxPlot}

	## example of call of child documents within a loop
	
    message(". Section box plot - via child documents using integer")

	locationBoxPlotDocument <- getPathTemplate("exampleTemplate_boxPlot.Rmd")
	
	# initialize the output
	outputBoxPlotDocument  <- NULL
	
    # variable for which to print box plots
    boxPlotVariables <- unique(dataset[,covariate]) 
  
	# loop across pairs of variables, with integer
	for(iBP in seq(length(boxPlotVariables))){

		# extract the code of the child, with variables within {{}} replaced
		outputBoxPlotDocument <- c(outputBoxPlotDocument, 
			knit_expand(locationBoxPlotDocument))
		
	}
	
	# run the document
	cat(knit(text = unlist(paste(outputBoxPlotDocument, collapse = '\n')), quiet=TRUE))

```

`r if(histogram)	"# Histogram"`

`r if(histogram)	paste("Note: we removed the '.' from the character since otherwise bookdown does not return figure numbers.")`

<!-- Via child documents using a character. -->


```{r histogram-viaLoopOnChildDocumentCharacter, eval = histogram}

	## example of call of child documents within a loop
	
    message(". Section histogram - via child documents using character")

	locationHistogramDocument <- getPathTemplate("exampleTemplate_histogram.Rmd")
	
	# initialize the output
	outputHistogramDocument  <- NULL
	
    # variable for which to print histogram
    histogramVariable <- gsub("\\.", " ", tolower(variables))
    histogramVariablesFull <- variables
    histogramVariablesDescription <- histogramVariable
    names(histogramVariablesFull) <- names(histogramVariablesDescription) <- histogramVariable
    
	# loop across pairs of variables, with character
	for(iH in histogramVariable){

	    iHST <- paste0("'", iH, "'")
	    
		# extract the code of the child, with variables within {{}} replaced
	    outputHistogramDocument <- c(outputHistogramDocument, 
			knit_expand(locationHistogramDocument))
		
	}
	
	# run the document
	cat(knit(text = unlist(paste(outputHistogramDocument, collapse = '\n')), quiet=TRUE))

```

`r if(pairwiseComparison)	"# Pairwise comparison plot"`

`r if(pairwiseComparison) 
	"## Summary\nFollowing Figure shows the correlation matrix of all variables contained in the data."`

```{r pairwiseComparison-summary, eval = pairwiseComparison}

	library(corrplot)
	inputCorrplot <- cor(dataset[, variables])
	corrplot.mixed(inputCorrplot, order = "hclust")

```
 
```{r pairwiseComparisonPlots-viaLoopOnChildDocumentInteger, eval = pairwiseComparison}
 
    message(". Section pairwise comparison - via loop on plots")
    message(".. Pairwise comparison plots via child documents using an integer")
 
	## path child template
    locationPairwiseComparisonPlotDocument <- 
		getPathTemplate("exampleTemplate_pairwiseComparison.Rmd")
 
	## input parameters

    # matrix with different pairs of variables (columns)
    pairwiseComparisonVariables <- combn(variables, 2)
 
    # description of the comparison as text
    pairwiseComparisonVariablesDescriptions <- apply(pairwiseComparisonVariables, 2, 
		paste, collapse = " and ")
     
	## run the document

    outputPairwiseComparisonPlotDocument  <- NULL # initialize the output
     
    # loop across pairs of variables, with character
    for(iPC in 1:ncol(pairwiseComparisonVariables)){
         
        # extract the code of the child, with variables within {{}} replaced
        outputPairwiseComparisonPlotDocument <- c(outputPairwiseComparisonPlotDocument, 
            knit_expand(locationPairwiseComparisonPlotDocument))
         
    }
     
    # run the document
    cat(knit(text = unlist(
		paste(outputPairwiseComparisonPlotDocument, collapse = '\n')), 
		quiet = TRUE)
	)
 
```

`r if(includeLda)	"# Linear discriminant analysis"`
`r if(includeLda)	knit_child(getPathTemplate("exampleTemplate_lda.Rmd"))`

# Appendix

## Used software

```{r usedSoftware}
		
	printSessionInfoMarkdown()
	
```

_Template developed by Kirsten Van Hoorde and Laure Cougnaud, Open Analytics._

