
```{r pairwiseComparisonChild-inputParameters-{{iPC}}}

	pairwiseComparisonVariablesDescription <- pairwiseComparisonVariablesDescriptions[{{iPC}}] # description
	
	pairwiseComparisonVariable <- pairwiseComparisonVariables[, {{iPC}}] # variables to compare
		
	colorVariable <- if(exists("pairwiseComparisonPlotColorVariable"))
		pairwiseComparisonPlotColorVariable # variable used for coloring
	
	if(!exists("typePlot"))	typePlot <- "rbokeh" # type plot
	
	message("Creation of pairwise comparison plot of ", pairwiseComparisonVariablesDescription, ".")

```

## Pairwise comparison of `r pairwiseComparisonVariablesDescription`

```{r pairwiseComparisonChild-correlationTest-{{iPC}}}

	resCorTest <- cor.test(
		x = dataset[, pairwiseComparisonVariable[1]], 
		y = dataset[, pairwiseComparisonVariable[2]]
	)

```

The **_Pearson_ correlation** between the
`r pairwiseComparisonVariablesDescription` is:
**`r round(resCorTest$estimate, 2)`** (p-value =
`r format(resCorTest$p.value, scientific = TRUE, digits = 2)`).

```{r pairwiseComparisonChild-extractData-{{iPC}}}
	
	# color palette
	library(oaColors)
	colorPalette <- oaPalette(
		numColors = ifelse(!is.null(colorVariable), nlevels(dataset[, colorVariable]), 1))
	names(colorPalette) <- levels(dataset[, colorVariable])

	figCaption <-  paste("Pairwise comparison of", pairwiseComparisonVariablesDescription)
	
```

Figure \@ref(`r paste0("fig:pairwiseComparisonChild-plots-", {{iPC}})`) shows
the pairwise comparison plot of `r pairwiseComparisonVariablesDescription`.

```{r pairwiseComparisonChild-plots-{{iPC}}, fig.cap = figCaption, results = ifelse(typePlot %in% c("rbokeh", "plotly"), 'markup', "asis")}
					
	pairwiseComparisonPlot(
		dataset = dataset, 
		variables = pairwiseComparisonVariable,
		description = pairwiseComparisonVariablesDescription,
		colorVariable = colorVariable, 
		colorPalette = colorPalette,
		typePlot = typePlot)
	
```