

```{r parametersChildDocument}

	## required input parameters
    message("Check required input parameters")

	# check if all require input parameters are specified
	variablesToSpecify <- c("dataset", "variables", "covariate")
	inputParametersNotSpecified <- !sapply(variablesToSpecify, exists)
	if(any(inputParametersNotSpecified))
		stop("Please specify the ", toString(variablesToSpecify[inputParametersNotSpecified]), ".")

	## optional input parameters, set to default value if not specified
    if(!exists("boxPlot")) boxPlot <- TRUE
    if(!exists("histogram")) histogram <- TRUE
	if(!exists("pairwiseComparisonPlot") & length(variables) > 1) pairwiseComparisonPlot <- TRUE
	if(!exists("includeLda") & length(variables) > 2) includeLda <- TRUE
	if(!exists("typePlot"))	typePlot <- "rbokeh"
	
```

```{r compareOutputpathWithWd}

    message("Compare output path with working directory")

	outputPathCompare <- paste0(getwd(), "/")
	if(.Platform$OS.type == "windows") outputPathCompare <- paste0("/", paste(unlist(strsplit(outputPathCompare, split = "/"))[-1], collapse = "/"),"/")

	differentWd <- outputPath != outputPathCompare
	
	if(differentWd) warning(paste0('The specified "outputPath" (i.e. ', outputPath,') is NOT the same \n as the current working directory (i.e. ', outputPathCompare, '). \n', 
		'The graphs and objects will be saved in the "outputPath" location, \n while the report (and the css file) will be saved in the working directory.'))
	
```

```{r copyCustomCssFile}

    message("Copy css file from package")

#	message("output path css: ", paste0(getwd(), "/css"))

	if(!exists("personalCss")) personalCss <- FALSE
	
	if(!personalCss){
		cssFile <- getPathFile("custom.css")
		outputPathCss <- paste0(getwd(), "/css")
		if(.Platform$OS.type == "windows") outputPathCss <- paste0("/", paste(unlist(strsplit(outputPathCss, split = "/"))[-1], collapse = "/"))
		if (!file.exists(outputPathCss)) dir.create(outputPathCss, recursive = TRUE)
		outputPathCss <- paste0(outputPathCss, "/")
		copyFile <- file.copy(from = cssFile, to = outputPathCss, overwrite = TRUE)
	}
  
    message(". Section Material and methods")

```


```{r outputDirectories}
	
	outputPathGraph <- paste0(outputPath, "graphs")
	if (!file.exists(outputPathGraph)) dir.create(outputPathGraph, recursive = TRUE)
	myGraphPath <- function(pathPlot){paste(outputPathGraph, pathPlot, sep = "/")}
	
	outputPathObjects <- paste0(outputPath, "objects")
	if (!file.exists(outputPathObjects)) dir.create(outputPathObjects, recursive = TRUE)
	myObjectPath <- function(pathObject){paste(outputPathObjects, pathObject, sep = "/")}

```

# Material and methods

## Data

The dataset contains `r nrow(dataset)` samples, `r length(variables)` variables:
`r toString(variables)`
and `r length(covariate)` covariate: `r toString(covariate)`.

```{r detailsOfData}

    message(".. Data table")

	library(DT)
	
	datatable(dataset, 
		options = list(
		searching = TRUE,
		pageLength = 10
#		lengthMenu = c(5, 10, 15, 20)
		),
		rownames = FALSE
	)
	
```

## Summary of the data

Tables below show overall statistics of `r toString(variables)` for:

*  the entire dataset
* the variables for each subset of the `r paste0("'", covariate, "'")`
  covariate:
`r paste(paste("    +", levels(dataset[,covariate])), collapse = "\n")`

<!-- Tables with pander in for loop. -->

```{r summaryDataPander}

  message(".. Summary of the data via pander")

  library(pander)
  panderOptions('knitr.auto.asis', FALSE)
  for(subData in c("all", levels(dataset[,covariate]))){
    
    if(subData == "all"){
      cat("\n### All", tolower(covariate), "\n\n")
      pander(summary(dataset[,variables]), caption = paste("Summary for all", tolower(covariate)))
    }else{
      cat("\n###", simpleCap(subData, onlyFirst = TRUE), "\n\n")
      pander(summary(dataset[dataset[,covariate] == subData,variables]), 
		caption = paste0("Summary for ", subData))
    }
    cat("\n\n")
    
  }

```

`r if(boxPlot)	"# Box plot"`

```{r boxPlots-viaLoopOnChildDocumentInteger, eval = boxPlot}

	## example of call of child documents within a loop
	
    message(". Section box plot - via child documents using integer")

	locationBoxPlotDocument <- getPathTemplate("exampleTemplate_boxPlot.Rmd")
	
	# initialize the output
	outputBoxPlotDocument  <- NULL
	
    # variable for which to print box plots
    boxPlotVariables <- unique(dataset[,covariate]) 
  
	# loop across pairs of variables, with integer
	for(iBP in seq(length(boxPlotVariables))){

		# extract the code of the child, with variables within {{}} replaced
		outputBoxPlotDocument <- c(outputBoxPlotDocument, 
			knit_expand(locationBoxPlotDocument))
		
	}
	
	# run the document
	cat(knit(text = unlist(paste(outputBoxPlotDocument, collapse = '\n')), quiet=TRUE))

```

`r if(boxPlot)	"# Histogram"`

<!-- Via child documents using a character. -->

Note: we removed the '.' from the character since otherwise bookdown does not
return figure numbers.

```{r histogram-viaLoopOnChildDocumentCharacter, eval = histogram}

	## example of call of child documents within a loop
	
    message(". Section histogram - via child documents using character")

	locationHistogramDocument <- getPathTemplate("exampleTemplate_histogram.Rmd")
	
	# initialize the output
	outputHistogramDocument  <- NULL
	
    # variable for which to print histogram
    histogramVariable <- gsub("\\.", " ", tolower(variables))
    histogramVariablesFull <- variables
    histogramVariablesDescription <- histogramVariable
    names(histogramVariablesFull) <- names(histogramVariablesDescription) <- histogramVariable
    
	# loop across pairs of variables, with character
	for(iH in histogramVariable){

	    iHST <- paste0("'", iH, "'")
	    
		# extract the code of the child, with variables within {{}} replaced
	    outputHistogramDocument <- c(outputHistogramDocument, 
			knit_expand(locationHistogramDocument))
		
	}
	
	# run the document
	cat(knit(text = unlist(paste(outputHistogramDocument, collapse = '\n')), quiet=TRUE))

```

`r if(pairwiseComparisonPlot)	"# Pairwise comparison plot"`

`r if(pairwiseComparisonPlot) 
	"## Summary\nFollowing Figure shows the correlation matrix of all variables contained in the data."`

```{r pairwiseComparison-summary, eval = pairwiseComparisonPlot}

	library(corrplot)
	inputCorrplot <- cor(dataset[, variables])
	corrplot.mixed(inputCorrplot, order = "hclust")

```
 
```{r pairwiseComparisonPlots-viaLoopOnChildDocumentInteger, eval = pairwiseComparisonPlot}
 
    message(". Section pairwise comparison - via loop on plots")
    message(".. Pairwise comparison plots via child documents using an integer")
 
	## path child template
    locationPairwiseComparisonPlotDocument <- 
		getPathTemplate("exampleTemplate_pairwiseComparison.Rmd")
 
	## input parameters

    # matrix with different pairs of variables (columns)
    pairwiseComparisonVariables <- combn(variables, 2)
 
    # description of the comparison as text
    pairwiseComparisonVariablesDescriptions <- apply(pairwiseComparisonVariables, 2, 
		paste, collapse = " and ")
     
	## run the document

    outputPairwiseComparisonPlotDocument  <- NULL # initialize the output
     
    # loop across pairs of variables, with character
    for(iPC in 1:ncol(pairwiseComparisonVariables)){
         
        # extract the code of the child, with variables within {{}} replaced
        outputPairwiseComparisonPlotDocument <- c(outputPairwiseComparisonPlotDocument, 
            knit_expand(locationPairwiseComparisonPlotDocument))
         
    }
     
    # run the document
    cat(knit(text = unlist(
		paste(outputPairwiseComparisonPlotDocument, collapse = '\n')), 
		quiet = TRUE)
	)
 
```

`r if(includeLda)	"# Linear discriminant analysis"`
`r if(includeLda)	knit_child(getPathTemplate("exampleTemplate_lda.Rmd"))`

# Appendix

## Used software

```{r usedSoftware}
		
	printSessionInfoMarkdown()
	
```

_Template developed by Kirsten Van Hoorde and Laure Cougnaud, Open Analytics._

